---
title: "Developing Data Product - Week 4 Assignment"
author: "Niharika"
date: "7 April 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction to Shiny App

- In this enclosed shiny app, iris data is used for data analysis.
- the graph of sepal length and sepal width is plotted with a UI to change the number of 
 instances to be plotted and max and min values of the x and y used in the graph. 
 

 What does the App do?

In this app, A slider is placed in sliderPanel which can be used to set the maximum and minimum values of the x and y axes. In mainPanel, a graph is made sepal length v/s sepal width. 

```{r results='hide', message=FALSE, warning=FALSE}
library(UsingR)
data("iris")
```

## Summary of The Galton Data

```{r echo=TRUE}
head(iris, 5)
summary(iris)
```

## Plot Used in The Shiny App

```{r echo=TRUE}
plot(iris$Sepal.Length, iris$Sepal.Width,  xlim = c(2, 10), ylim = c(0,6))
```

## Instructions for Usage

- Clone the code using 'git clone https://github.com/Niharika1203/DDP_WEEK4_ASSIGNMENT.git  'YOURDIRECTORY'
- Load your RStudio
- Set your working directory to YOURDIRECTORY using setwd("YOURDIRECTORY")
- Load the Shiny library using library(shiny)
- Load the UsingR library using library(UsingR)
- Run the application using runApp()
Step7) You will see the application in a browser.